\begin{essay}
  % My intro paragraph
  When I was younger, about $8$ - $9$ years old, I enjoyed watching shows like
  \textbf{Popular Mechanics} and \textbf{National Geographic}. Unfortunately, I
  regretted watching one of the \textbf{National Geographic} videos for almost
  $2$ years. The video talked about sinkholes, which terrorized me. Since I was
  a very optimistic, naive little kid who didn't think anything was wrong in the
  world, this took its toll on me. My bubble of a world shook. The world wasn't
  all flowers and roses anymore. From fire and flames to floods and light
  beaming from the sky, I created many dark ideas about how the world may end.
  From that day on, I imagined every day as the last day, spending countless
  hours reading about sinkholes. Every time I tried to sleep, I would hear the
  piercing sound coming from the sinkholes and visually see it as if I was
  falling into one. My family forbade me from reading any more books on the
  matter. Eventually, like all little kids, I grew out of this phobia, but life
  after was different.

  % Inline etymological definition of the term apocalypse
  The online etymological dictionary defines the term \textbf{Apocalypse} as
  \textit{a cataclysmic event}. TODO: Expand here

  % Talk about the Quranic End of Times
  A smoke so thick you cannot see your hand, even if it's an inch from your
  face, covers the entire atmosphere. A beast comes to talk to you while there
  are earthquakes shaking the entire world. Fires ravage from Yemen, which
  forces everybody to one location. This is how the Islamic religion depicts the
  end of times. I grew up with this story of how the end of times will commence.
  I didn't really take it too seriously, but eventually, I decided to learn more
  about this prophecy. There are things called \textbf{Hadith}, which are the
  sayings and teachings of Prophet Muhammad and they're given ranks, where the
  highest is the most reliable and most trust worthy Hadith, while the lowest
  being not fake, but more on that spectrum. A Hadith, that is placed on the
  higher ranks narrates that after Prophet Muhammad lead the morning prayer
  (\textbf{fajir}), which is around $4$ AM, he got on his mimbar and he preached
  until the noon prayer (\textbf{duhr}), which is around $1$ PM. After they
  finished praying, he got back up and preached until the next prayer, and the
  next and the final prayer, which is around $11$ PM. He's describing the end of
  times. You can find dozens of volumes of books talking about this subject and
  that doesn't even cover half of everything. There are two chapters in the
  Quran which are dedicated to talking about this specific event. The first one,
  Al-Waqiah, which means \textbf{The Inevitable} and Al-Qiyamah, which means
  \textbf{The Resurrection}. Prophet Muhammad stated that the End of Days won't
  happen until you see the $10$ signs. The first sign is a thick smoke that will
  cover our entire atmosphere. After that, the Dajjal, or Anti-Christ will come
  while a beast comes to talk to the people. One of the most dangerous signs is
  when the sun rises and sets on opposite directions. The reason this is
  dangerous is because when this happens, Allah won't forgive anybody and if
  anybody wants to become Muslim after this event, it won't be accepted. Then,
  Jesus PBU descends to kill the Dajjal, which is right before the Gog and Magog
  arrival. The next sign are a group of $3$. $3$ earthquakes shake the entire
  earth. One in the East, one in the West, and one in the Arabian Peninsula. The
  final one is a fire from Yemen will start to gather all the people around the
  world to the place called Mahshar, which means the gather place. This is where
  the people will be resurrected for the day of judgment. Prophet Muhammad said
  if you see only one of these signs, be prepared to see the next ones very
  soon. While all of these signs are happening, the world will split into $2$
  categories. Muslims vs Christians. The Prophet Muhammad called this war the
  \textbf{Great War}. He also said that there will be no affliction that will be
  worse than this war. I'm not going to go in detail because I would end up
  writing an entire volume of books, but a key highlight is when the people are
  gathered in the Mahshar, a breeze will come down and whoever has an ounce of
  faith will die peacefully while the non-believers will die later on. After
  every body dies, Allah folds the entire Universe with one hand and the other
  $6$ universes with the other. After a while, he calls everybody to be judged
  for what they have done.

  On the note of apocalyptic events, one of my favorite apocalyptic movie is the
  \textbf{Train to Busan}. The main plot of the movie is about a father and his
  daughter trying to make their way across \textbf{South Korea}, via a train,
  when, out of nowhere, a virus starts to spread among the passengers. The
  father is always a busy man, who works in stocks or something, while the
  little girl is always alone because her parents divorced. After the movie, you
  can see how the father transformed from always worrying about work and his
  money to dying to save his daughter's life. If you were to take the father
  from the beginning of the movie and place him at the end where he had to risk
  his life for his daughter, he wouldn't have risked his own life. Personally, I
  believe that the events that he and his daughter went through throughout the
  movie are what shaped him. The virus that spreads on the train kills the
  victim and transforms them into a zombie. The movie focuses on different
  aspects, which other zombie movies may not. It criticizes society on many
  levels, one being, how humans are and how an event so colossal as an
  apocalypse can show their true skin. The characters in the movie make this
  movie distinct because they're very likable people since they aren't horrible
  to other people and selfless. Usually, in apocalyptic movies, the main
  character survives by sheer luck. In the Train to Busan movie, you would
  assume that the characters who survive are the ones who manipulate and use
  others for their own survival. Ironically, the selfless people are the ones
  who survive in the end and all of the followers and the cruel people end
  dying. This aspect is what makes this movie really make it unique in its own
  way.

  Initially, I assumed that the term \textbf{Apocalypse} meant the end of the
  world. Although that definition is a worldwide accepted meaning, there are
  other definitions and interpretations. One interpretation may be \textit{an
  Apocalypse brings out the true color in people.} It will help you distinguish
  your friends from your enemies and vice versa. Also, an apocalypse may be the
  end of a chapter and the beginning of something new like how all the religious
  scriptures say. Even in the \textbf{Train to Busan}. The apocalypse may start
  something new like a discovery about something from a different world. That's
  also the main theme for the Quranic end of times. During the \textbf{Day of
  Judgment}, which different than the \textbf{End of Times}, people will be
  questioned for their actions. Prophet Muhammad stated that a mother will start
  to blame some of her sins on her child if she has to, to get out of being
  punished for them. One thing that struct me the most was how my fear of
  sinkholes started to reveal to me about a world that I never knew, one that no
  religious text, or even apocalyptic movies/books can display. My fear of
  sinkholes gathered my family together to help me, even if it's not the best
  way possible. On the other hand, the Quranic text shows what will happen in
  the far out future while my fear displayed fears of everyday life. The Train
  to Busan displayed that really well for me because the virus just appeared out
  of nowhere, which is what I thought would happen with sinkholes. Overall, I'm
  glad that I went through with the troubles since it helped develop my
  personality and widen my view of the world.
\end{essay}
