\lesson{4}{Sep 22 2021 Wen (10:51:32)}{Citizenship Review}{Unit 1}

\subsubsection*{Vocabulary Review}

Let's quickly go over the basic vocabulary for this unit:

\begin{definition}[Common Good]
    The common good is the greatest possible conditions of society for the greatest number of people living in it. Citizens serve their community to improve life for people in general.
\end{definition}

\begin{definition}[Institution]
    An institution is an established organization that is influential in the community such as a school or hospital. Government helps support the creation and maintenance of many important institutions.
\end{definition}

\begin{definition}[Rule of Law]
    Rule of law is the principle that both those who govern and those who are governed must obey the law and are subject to the same laws. Government leaders resolve problems based on the law.
\end{definition}

\begin{definition}[Limited Government]
    Limited government is the idea that government should be restricted to its basic function of protecting people`s natural rights. Leaders without limits could rule without concern for the people.
\end{definition}

\begin{definition}[Representative Government]
    Representative government is a form of government where the people elect leaders to make decisions on their behalf, sometimes called a republic. The United States has this form of government.
\end{definition}

\begin{definition}[Consent of the Governed]
    Consent of the governed is the idea that people agree, or consent, to government authority and in return, the government protects the people and their rights, also known as the social contract.
\end{definition}

\begin{definition}[Natural Rights]
    Natural rights are rights that people are born with and that no government can take away. U.S. citizens value and hold these rights as individuals.
\end{definition}

\begin{definition}[Green Card]
    A green card is a government identification card giving legal permission to an immigrant to live and work in the United States permanently. It is an important prerequisite to naturalization.
\end{definition}

\begin{definition}[Naturalization]
    Naturalization is the legal process for non-native residents to become U.S. citizens. Immigrants must meet several requirements to become citizens, including knowing basic English.
\end{definition}

\begin{definition}[Public Policy]
    A public policy is a course of action accepted or used by a government to respond to a problem. Public policy determines the naturalization process and many other activities in our daily lives.
\end{definition}

\newpage