\chapter{Algebra Review}
\label{chap:algebra_tools_needed_to_study_trigonometry}

Basic algebra and trigonometry deal with two different areas of mathematics.
Many people believe that trigonometry is a completely different discipline than
algebra. But the truth is that isn't really the truth. You cannot fully
comprehend trigonometry without knowing the basis of algebra, making algebra a
prerequisite to trigonometry.

Algebra deals with finding the unknown variables and understanding functions --
whereas trigonometry explores aspects of triangles, which are their sides and
angles and finding a correlation between them. Algebra seeks to solve equations
composed of multiple terms and to find their roots, whereas trigonometry
focuses mainly on sin, cos, tan, degrees, radians, and polar coordinates.

It's helpful to imagine trigonometry as an extension to algebra because we
often treat trigonometric concepts in algebraic terms. For example, solving a
trigonometric equation is similar to solving an algebraic equation. You also
learn the basic rules of vital topics like polynomials, exponents, graphing and
much more in algebra. However, despite their similarities, there are still a
number of differences. They are still both prerequisites to more advanced
mathematical topics like calculus and differential equations.

\section{Cartesian Coordinates}
\label{sec:cartesian_coordinates}

In algebra, you use the standard Cartesian coordinate system when graphing
various functions. One of the most common methods of solving systems of
equations is graphing them, where the solution is the point of intersection in
all the lines.

\begin{definition}[Cartesian Coordinate System]
  \label{def:cartesian_coordinate_system}

  The \textbf{cartesian coordinate system} specifies each point on a plane by a
  pair of numerical coordinates, which are distances from the point to two
  fixed perpendicular lines, commonly referred to as the $x$-axis and $y$-axis.
\end{definition}

The simplest coordinate system is a number line on which you represent numbers.
Next, we represent ordered pairs of numbers in a plane on which two of these
lines are located.

In plane geometry, there are two axes at right angles that are usually called
$x$-axis and $y$-axis. The position of any point in the plane can be given by
its two coordinates $(x, y)$. These coordinates give the point's distance in
the $x$ and $y$ directions from the origin, which is the point of intersection
of the two axes. The origin is labeled with the pair of numbers both at zero --
$(0, 0)$.

\subsection{Writing Coordinates}
\label{sub_sec:writing_coordinates}



% subsection writing_coordinates (end)

% section cartesian_coordinates (end)

% chapter algebra_tools_needed_to_study_trigonometry (end)

\newpage
