\lesson{5}{Mar 03 2022 Thu (18:38:15)}{Word problem involving average rate of change}{Unit 1}

\begin{definition}[Slope]
  \label{def:slope}
  
  The slope of a line is a number measuring how \textbf{Steep} the line is.

  The farther the slope is from zero, the steeper the line is. The slope of a
  vertical line is undefined.

  The sign of the slope tells us if the line will go \textbf{up} or
  \textbf{down}.

  \begin{itemize}
    \label{item:slope_sign}

    \item If the slope is \textbf{positive}, then the line goes upward from
      \textbf{left} to \textbf{right}.
    \item If the slope is \textbf{negative}, then the line goes
      \textbf{downward} from \textbf{left} to \textbf{right}.
    \item If the slope is $0$, then the line is \textbf{horizontal}.
  \end{itemize}

  Suppose that a non-vertical line passes through the two points:
  $\left(x_1, y_1\right), \left(x_2, y_2\right)$ 

  The \textit{rise} from the first point to the second is $y_2 - y_1$.

  The \textit{run} from the first point to the second is $x_2 - x_1$

  The slope formula is:

  \begin{equation}
    \label{eqt:slope_formula}
    \begin{split}
      \textrm{slope} \quad = \quad \frac{\textrm{rise}}{\textrm{run}} \quad =
        \quad \quad \frac{y_2 - y_1}{x_2 - x_1}
    \end{split}
  .\end{equation}
\end{definition}

The number of bacteria in a culture increase rapidly. The table below gives
the number $N(t)$ of bacteria at a few times $t$ (in hours) after the moment
when $N = 1000$.

\begin{table}[H]
  \centering
  \label{tab:bacteria_number}

  \begin{tabular}{|c|c|}
    \hline
    Time $t$ hours & Number of bacteria $N(t)$ \\ \hline
    $0$ & $1000$ \\ \hline
    $3.4$ & $1510$ \\ \hline
    $6.8$ & $2292$ \\ \hline
    $10.2$ & $3856$ \\ \hline
    $13.6$ & $5080$ \\ \hline
  \end{tabular}
\end{table}

\begin{enumerate}
  \label{item:what_we_are_going_to_do}

  \item We're going to find the \gls{arc} for the number of bacteria from
    $0$ hours to $6.8$ hours.
  \item Find the \gls{arc} for the number of bacteria from $10.2$ 
    hours to $13.6$
\end{enumerate}

The \gls{arc} for the number of bacteria from $t = a$ to $t = b$
is:

\begin{equation}
  \label{eqt:average_rate_of_change}
  \begin{split}
    \frac{N(b) - N(a)}{b - a}, \quad \textrm{where} \quad b \ne a \\
  \end{split}
.\end{equation}

\begin{note}
  \label{nte:average_rate_of_change_note}

  Look how similar the equation above (\ref{eqt:average_rate_of_change}) is
  similar to the slope (\ref{def:slope}) formula.
\end{note}

The \gls{arc} is the slope of the line passing through:
$(a, N(a)) \quad (b, N(b))$.

\begin{enumerate}
  \label{enum:average_rate_of_bacteria_steps}

  \item For part \textbf{A}, we're asked to find the \gls{arc} from $0$ hours to
    $6.8$ hours.

    So we take $a = 0 \quad b = 6.8$.

    From the table, we get $N(a) = 1000 \quad N(b) = 2292$.

    Applying the formula for \gls{arc}, we get:

    \begin{equation}
      \label{eqt:average_rate_of_change_bacteria}
      \begin{split}
        \frac{N(b) - N(a)}{b - a} &= \frac{2292 - 1000}{6.8 - 0} \\
                                  &= \frac{1292}{6.8} \\
                                  &= \boxed{190 \quad \textrm{Bacteria per Hour}}
      \end{split}
    .\end{equation}

  \item For part \textbf{B}, we're asked to find the \gls{arc} from $10.2$ hours
    to $13.6$ hours.

    So, we take $a = 10.2 \quad b = 13.6$.

    From the table, we get $N(a) = 3856 \quad N(b) = 5080$.

    Applying the formula for \gls{arc}, we get:

    \begin{equation}
      \label{eqt:average_rate_of_change_bacteria_2}
      \begin{split}
        \frac{N(b) - N(a)}{b - a} &= \frac{5080 - 3856}{13.6 - 10.2} \\
                                  &= \frac{1224}{3.4} \\
                                  &= \boxed{360 \quad \textrm{Bacteria per Hour}}
      \end{split}
    .\end{equation}
\end{enumerate}

So, our final answers are:

\textbf{The \gls{arc} for the number of bacteria from $0$ hours to $6.8$ hours
is}: \\
\boxed{$190 \quad$ \textbf{Bacteria per hour}}

\textbf{The \gls{arc} for the number of bacteria from $10.2$ hours to $13.6$ hours
is:} \\
\boxed{$360 \quad$ \textbf{Bacteria per hour}}

\newpage
