\lesson{8}{Mar 18 2022 Fri (16:35:01)}{Domain and range of a linear function}{Unit 1}
\label{les_8_unit_1:domain_and_range_of_a_linear_function}

\begin{definition}[Domain]
  \label{def:domain}

  The domain of a function is the set of all possible inputs.
\end{definition}

\begin{definition}[Range]
  \label{def:range}

  The domain of a function is the set of all possible inputs of the function.
\end{definition}

\begin{example}
  \label{exm:domain}

  Suppose that the function $f$ is defined by the following table:

  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      x & $f(x)$ \\ \hline
      $1$ & $1$ \\ \hline
      $2$ & $8$ \\ \hline
      $3$ & $27$ \\ \hline
      $4$ & $64$ \\ \hline
    \end{tabular}
  \end{center}

  The domain of $f$ is the set of numbers in the left column. The range of the
  function $f$ is the set of numbers in the right column. That is:

  \begin{equation}
    \label{eqt:domain_range}
    \begin{split}
      \textrm{Domain:} \quad f = \{ 1, 2, 3, 4 \} \\
      \textrm{Range} \quad f = \{ 1, 8, 27, 64 \} \\
    \end{split}
  .\end{equation}

  The function $f$ 
  could also be written as a set of ordered pairs:

  \[ f(x) = \{(1, 1), (2, 8), (3, 27), (4, 64)\} \].

  Here's a cooler way of showing it:

  \begin{equation}
    \label{eqt:domain_range_cool}
    \begin{split}
      f(x) = 3x, x \in [-2, 5]
    \end{split}
  .\end{equation}

  The statement above (\ref{eqt:domain-range-cool}) is saying that the domain
  of the function $f(x)$ is the interval (\ref{def:interval}) $[-2, 5]$
\end{example}

\begin{note}
  \label{nte:domain_range_pairs}

  Note that the domain is the set of all first elements in the ordered pairs,
  and the range is the set of all second elements in ordered pairs.
\end{note}

\begin{example}
  \label{exm:domain_range}

  A construction crew is lengthening the road. Let $L$ be the total length of
  the road (in miles). Let $D$ be the number of days the crew has worked.

  Suppose that $L = 4D + 400$ gives $L$ as a function of $D$. The crew can work
  for at most $70$ days.

  Identify the correct description of the values in both the domain and range of
  the function.

  Here's how we would approach such a problem:

  We are given the function: $L = 4D + 400$. Here, $L$ is the total length of
  the road and $D$ is the total number of days the crew has worked.

  \subsubsection{Domain}
  \label{sub_sub_sec:domain}

  \paragraph{Description of values for the domain}
  \label{par:description_of_values_for_the_domain}

  For our function, the input is given by $D$.
  So, the values in the domain correspond to the number of days the crew has
  worked.
  
  % paragraph description_of_values_for_the_domain (end)

  \paragraph{Set of values for the domain}
  \label{par:set_of_values_for_the_domain}

  We are given that the crew can work for at most $70$ days.
  
  So, our domain will be $[0, 70]$.

  % paragraph set_of_values_for_the_domain (end)
  
  % subsubsection domain (end)

  \subsubsection{Range}
  \label{sub_sub_sec:range}
  
  \paragraph{Description of Values for the Range}
  \label{par:description_of_values_for_the_range}
  
  For our function, the output is given by $L$.
  So the values in the range correspond to the total length of the road.

  \subparagraph{Set of Values for the Range}
  \label{sub_par:set_of_values_for_the_range}
  
  To find the range, let's look at the output $L$ for some values of $D$:

  After $0$ days, the total length of the road will be:
  $L = 4(0) + 400 = 400 \quad \textrm{miles}$ 

  After $1$ day, the total length of the road will be:
  $L = 4(1) + 400 = 401 \quad \textrm{miles}$

  After $10$ day, the total length of the road will be:
  $L = 4(10) + 400 = 440 \quad \textrm{miles}$
  
  After $20 \frac{1}{2}$ day, the total length of the road will be:
  $L = 4(20 \frac{1}{2}) + 400 = 482 \quad \textrm{miles}$

  After $70$ day, the total length of the road will be:
  $L = 4(70) + 400 = 680 \quad \textrm{miles}$

  Note also that we can get any length between $400$ and $680$ miles for the
  road.

  So, we choose all of the real numbers between $400$ and $680$ miles.

  Or, we can write it like this:

  \begin{equation}
    \label{eqt:values_for_the_range}
    \begin{split}
      L \in [400, 680]
    \end{split}
  .\end{equation}
  
  % subparagraph set_of_values_for_the_range (end)
  
  % paragraph description_of_values_for_the_range (end)
  
  % subsubsection range (end)
\end{example}

\begin{note}
  \label{nte:set_of_values_for_the_domain}

  The number of days must also be $x \ge 0$.

  The number of days could also be decimals, fractions, etc like:
  $\frac{1}{2} \quad \frac{10}{19} \quad \frac{7}{11} \quad \frac{11}{7}$

  The only restriction we have is that the number of days must be $x \ge 0$
\end{note}

\newpage
