\doublespacing

% Question: How does an understanding of natural rights and respect build a free society?

% Intro:

A free society is constructed from two core ideas: Natural rights and
respect. Natural rights are those that are independent from any government,
which makes them universal and indisputable. No man or government should take
those away. Respect is required since it establishes a secure society for people
to be themselves, which in turn, makes the society free, but yet, flourish. If
you don't

% Body 1: Defines natural rights

English Philosopher, Physician, and Scholar, John Locke first presented with the
idea of natural rights in $1689$. He stated

\begin{center}
	\begin{quotation}
		\textit{"The state of Nature has a law of Nature to govern it, which obliges
			every one, and reason, which is that law, teaches all mankind who will but
			consult it, that being all equal and independent, no one ought to harm
			another in his life, health, liberty or possessions; for men being all the
			workmanship of one omnipotent and infinitely wise Maker; all the servants
			of one sovereign Master, sent into the world by His order and about His
			business; they are His property, whose workmanship they are made to last
			during His, not one another’s pleasure. And, being furnished with like
			faculties, sharing all in one community of Nature, there cannot be
			supposed any such subordination among us that may authorise us to destroy
			one another, as if we were made for one another’s uses, as the inferior
			ranks of creatures are for ours. Every one as he is bound to preserve
			himself, and not to quit his station wilfully, so by the like reason, when
			his own preservation comes not in competition, ought he as much as he can
			to preserve the rest of mankind, and not unless it be to do justice on an
			offender, take away or impair the life, or what tends to the preservation
			of the life, the liberty, health, limb, or goods of another."}
		(\cite{noauthor_right_nodate})
	\end{quotation}
\end{center}

\noindent He characterized these rights as \textit{"Life"}, \textit{"Liberty"},
and \textit{"Property"}. Later on, the US would make it part of the Constitution
to protect these rights. The founding fathers adhered to the idea that without
permitting their citizens their natural rights, their country won't be free,
which, in turn, is bound would make their citizens bound to rebel.

% Body 2: Affects of people not understanding their natural rights

In today's society, if you don\'t understand your natural rights, you're bound to
have them taken away.

% Body 3: Affects of people understanding their natural rights

% Body 4: Affects of people not having respect

% Body 5: Affects of people having respect

% Body 6: How do they both create a free society

% Conclusion:
