People love to debate on whether Brutus is a traitor for killing Caesar, or if
he’s a patriot for doing what he thinks is right to save Rome. Let’s start here.
What exactly is a traitor. The definition of the word \textbf{Traitor} means:
\textit{"A person who betrays a friend, country, principle, etc."} and the
definition for the word \textbf{Patriot} is: \textit{"A person who vigorously
supports their country and is prepared to defend it against enemies or
detractors."}

Most people would agree that Brutus was a traitor, since he killed his friend,
which was the Roman King. Instead of trying to think of a plan to stop Caesar
from destroying Rome, he just decided to kill his friend, whose the king to take
his place. Caesar couldn’t believe that his friend, Brutus, had stabbed him.
That shows how strong their friendship was. But, you have to take into
consideration Brutus’s intentions. He claims that he killed Caesar for the good
of Rome. He stated that his love for his country outweighed his love for a
single man. He also stated that Caesar was a great leader, but ambitious.

Also, if you look towards the end of the act, Brutus kills himself. There are
multiple reasons why. The first reason is because he feels guilty for what he
did and he wanted Caesar to be avenged. Another reason is because he notices the
mistake of what he’s done and the consequences of it. So, in order to fix his
mistakes, he ends his life. The last thing he notices is that Antony is a person
whose better fit for the throne of Rome. So, he takes his life, which avenges
Caesar, fixes the mistake that he’s done, and gives the throne to Antony. So, in
essence, he’s killing himself for the sake of Rome. If we look back at our
definition of the word Patriot, that’s what it means. You give everything for
your country, which is exactly what Brutus did.

In conclusion, Brutus was a Patriot because of his love for his country.
Although he could have done things differently, his intention was pure, and we
got to see his regret while killing himself for what he’s done.
