People love to debate on whether Brutus is a traitor for killing Caesar, or if
he's a patriot for doing what he thinks is right to save Rome. Let's start here.
What exactly is a traitor. The definition of the word \textbf{Traitor} means:
\textit{"A person who betrays a friend, country, principle, etc."} and the
definition for the word \textbf{Patriot} is: \textit{"A person who vigorously
supports their country and is prepared to defend it against enemies or
detractors."} From these definitions, we see that Brutus, was, in fact, a
\textbf{Patriot}.

Most people would agree that Brutus was a traitor, since he killed Caesar.
Instead of trying to think of a plan to stop him from not becoming king of Rome,
he just decided to kill his friend, to take his place. When Brutus finally
stabbed Caesar, he couldn't believe that his friend, Brutus, had stabbed him.
That shows how strong their friendship was. But, you have to take into
consideration Brutus's intentions. He claims that he killed Caesar for the good
of Rome. He stated that his love for his country outweighed his love for a
single man.

\begin{center}
  \begin{quotation}
    Be not deceived. If I have veiled my look, I turn the trouble of my
    countenance Merely upon myself. Vexe\'d I am Of late with passions of some
    difference, Conceptions only proper to myself, Which give some soil perhaps
    to my behaviors. But let not therefore, my good friends, be grieved— Among
    which number, Cassius, be you one— Nor construe any further my neglect Than
    that poor Brutus, with himself at war, Forgets the shows of love to other
    men.
  \end{quotation}
\end{center}

He also stated that Caesar was a great leader, but ambitious.

\begin{center}
  \begin{quotation}
    When that the poor have cried, Caesar hath wept: Ambition should be made of
    sterner stuff: Yet Brutus says he was ambitious; And Brutus is an honourable
    man.
  \end{quotation}
\end{center}

\noindent If we go back to our definitions, we can see that the word
\textbf{Patriot} best describes his intentions.

Another compelling action of Brutus his his suicide towards the end. There are
multiple reasons why. The first reason is because he feels guilty for what he
did and he wanted Caesar to be avenged.

\begin{center}
  \begin{quotation}
    Caesar, now be still. \\
    I killed not thee with half so good a will
  \end{quotation}
\end{center}

\noindent Another reason is because he notices the mistake of what he's done and
the consequences of it. So, in order to fix his mistakes, he ends his life. The
last thing he notices is that \textbf{Antony} is a person whose better fit for
the throne of Rome. So, he takes his life, which avenges Caesar, fixes the
mistake that he's done, and gives the throne to \textbf{Antony}. So, in essence,
he's killing himself for the sake of Rome. If we look back at our definition of
the word \textbf{Patriot}, that's what it means. You give everything for your
country, which is exactly what Brutus did.

In conclusion, Brutus was a \textbf{Patriot} because of his love for his
country. Although he could have done things differently, his intention was pure,
and we got to see his regret while killing himself for what he's done.

