\subsection{Hypothesis}

I predict that:

\begin{itemize}
  \item \bf{Vinegar} will be \bf{Polar}
  \item \bf{Vegetable Oil} will be \bf{Non-Polar}
  \item \bf{Salt} will be \bf{Ionic}
  \item \bf{Water} will be \bf{Polar}
  \item \bf{Rubbing Alcohol} will be \bf{Non-Polar}
\end{itemize}

\subsection{Variables}

\begin{itemize}
  \item \bf{Controlled Variable} is \bf{Amount of substance to be tested}
  \item \bf{Independent Variable} is \bf{The substance being tested}
  \item \bf{Dependent Variable} is the \bf{Polarity}
\end{itemize}

\subsection{Data}

\begin{itemize}
  \item \bf{Vinigar} and \bf{Water}:
    Soluble \\
    \bf{Vinegar} is \bf{Polar} \\
    \bf{Water} is \bf{Polar}

  \item \bf{Iodine Solution} and \bf{Water}:
    Soluble \\
    \bf{Iodine Solution} is \bf{Non-Polar} \\
    \bf{Water} is \bf{Polar}

  \item \bf{Rubbing Alcohol} and \bf{Vegetable Oil}:
    Soluble \\
    \bf{Rubbing Alcohol} is \bf{Polar} \\
    \bf{Vegetable Oil} is \bf{Non-Polar}

  \item \bf{Salt} and \bf{Vegetable Oil}:
    Insoluble \\
    \bf{Salt} is \bf{Ionic} \\
    \bf{Vegetable Oil} is \bf{Non-Polar}

  \item \bf{Water} and \bf{Rubbing Alcohol}:
    Soluble \\
    \bf{Water} is \bf{Polar} \\
    \bf{Rubbing Alcohol} is \bf{Polar} \\

  \item \bf{Vinegar} and \bf{Rubbing Alcohol}:
    Soluble \\
    \bf{Vinegar} is \bf{Polar} \\
    \bf{Rubbing Alcohol} is \bf{Polar} \\

  \item \bf{Iodine Solution} and \bf{Vinegar}:
    Insoluble \\
    \bf{Iodine Solution} is \bf{Non-Polar} \\
    \bf{Vinegar} is \bf{Polar} \\

  \item \bf{Vegetable Oil} and \bf{Vinegar}:
    Insoluble \\
    \bf{Vegetable Oil} is \bf{Non-Polar} \\
    \bf{Vinegar} is \bf{Polar} \\
\end{itemize}

\subsection{Conclusion}

Write a conclusion statement that addresses the following questions:

\begin{itemize}
  \item Which of your polarity and solubility predictions were correct? \\
    \bf{They were all correct. }
  \item How do you think the investigation can be explored further? \\
    \bf{I don’t think this investigation can be explored further.}
\end{itemize}

\section{Post-Lab Reflection Questions}

Answer the reflection questions using what you have learned from the lesson and
your experimental data. It will be helpful to refer to your chemistry journal
notes. Answer questions in complete sentences.

\begin{itemize}
  \item How do models help scientists predict the polarity of molecules?
    \bf{Molecular models are representations of a molecule. A molecule may
        contain polar bonds but may not have an overall dipole moment because of its
        structure. The possession of polar bonds alone isn’t enough to determine the
        polarity of a molecule. The molecular model gives a picture of the molecule and
        ultimately determines whether the molecule will have a dipole moment, which
        indicates if it’s a polar molecule or a nonpolar molecule.}
\end{itemize}
