\lesson{29}{Mar 30 2022 Wed (12:06:56)}{Rejecting unreasonable claims based on average statistics}{Unit 7}

\begin{definition}[Percentage of Profit]
  \label{def:percentage_of_profit}

  Percentage of profit of the client is the sum of their percentage profits,
  divided by the number of clients.
\end{definition}

An investment company advertised that last year its clients, on average,
made a profit of $8 \%$. What is true about this statement:

\begin{itemize}
  \label{item:possible_answers}

  \item Last year, the number of clients who made a profit of $8 \%$ or
    more was equal to the number of clients who made a profit of $8 \%$ or
    less.
  \item Two years ago some of their clients made a profit of less than
    $8 \%$.
  \item Last year some of their clients made a profit of at least $8 \%$.
  \item Last year at least one of their clients made a profit of more than $3
    \%$.
  \item Last year at least one of their clients made a profit of exactly
    $8 \%$.
\end{itemize}

We were told to assume that average refers to the mean, and in fact this is
the most common use of the word average.

\subsubsection{First Possible Answer}
\label{sub_sub_sec:first_possible_answer}

The first statement is not necessarily true. For example, if the
company had only three clients who made profits of $7 \%$, $7 \%$, and $10
\%$ last year, the average would be $8 \%$, but the number of clients who
made profit of $8 \%$ or more last year would not be equal to the number
of their clients who made a profit of $8 \%$ or less that year, which
makes this statement not necessarily true.

% subsubsection first_possible_answer (end)

\subsubsection{Second Possible Answer}
\label{sub_sub_sec:second_possible_answer}

We know that the clients of the investment company made an average
profit of $8 \%$ last year. But, we don't know for sure how the clients of
the company did two years ago, which makes the second answer not
necessarily true.

% subsubsection second_possible_answer (end)

\subsubsection{Third Possible Answer}
\label{sub_sub_sec:third_possible_answer}

If every client made a profit of less than $8 \%$ last year, then the
average profit couldn't be $8 \%$. From this, we know that some of their
clients must have made a profit of at least $8 \%$ last year, which makes
the third answer true.

% subsubsection third_possible_answer (end)

\subsubsection{Fourth Possible Answer}
\label{sub_sub_sec:fourth_possible_answer}

If every client made a profit of $3 \%$ or less last year, then the
average profit could not be near $8 \%$. From this, we know that some of
their clients must have made a profit more than $3 \%$ last year, which
makes the fourth answer true.

% subsubsection fourth_possible_answer (end)

\subsubsection{Fifth Possible Answer}
\label{sub_sub_sec:fifth_possible_answer}

If the company had only two clients who made profits of $7 \%$ and $9
\%$ last year, the average would be $8 \%$, but no client would have made
a profit of exactly $8 \%$, which makes the final answer not necessarily
true.

% subsubsection fifth_possible_answer (end)

\subsubsection{Final Answer(s)}
\label{sub_sub_sec:final_answer_s_}


So, here are our final answers:

\begin{itemize}
  \label{item:final_answers}

  \item Last year some of their clients made a profit of at least $8 \%$.
  \item Last year at least one of their clients made a profit of more than
    $3 \%$.
\end{itemize}

% subsubsection final_answer_s_ (end)

\newpage
