\lesson{15}{Mar 18 2022 Fri (23:06:17)}{Probability of dependent events}{Unit 7}

A department store is holding a drawing to give away free shopping sprees. There
are $10$  customers who have entered the drawing: $4$ live in the town of
Gaston, $4$ live in Pike, and $2$ live in Wells. Two winners will be selected at
random. What is the probability that both winners live in Wells? Write your
answer as a fraction in simplest form.

We can think of there being a "first winner" and a "second winner." Whether the
first winner lives in Wells affects the probability that the second winner lives
in Wells. These two events are dependent.

if $A$ and $B$ are dependent events, then the probability that they both occur
can be computed as follows.

\begin{equation}
  \label{eqt:probability_of_A_and_B}
  \begin{split}
    P(\textrm{$A$ and $B$}) = P(A) \times P(\textrm{$B$ Given $A$})
  \end{split}
.\end{equation}

Before the first winner is selected, there are $10$  customers to choose from,
and $2$  of them live in Wells. So we have:

\begin{equation}
  \label{eqt:two_to_choose_from}
  \begin{split}
    P(\textrm{"First winner lives in Wells"}) = \frac{2}{10} \times \frac{1}{5}
  \end{split}
.\end{equation}

If the first winner lives in Wells, then there will be $1$ customer who lives in
Wells in the remaining $9$ customers. So we have:

\begin{equation}
  \label{eqt:remaining_customers}
  \begin{split}
    P(\textrm{"Second winner lives in Wells" given "First winner lives in
    Wells"}) = \frac{1}{9}
  \end{split}
.\end{equation}

We can now compute the probability that both winners live in Wells.

\begin{equation}
  \label{eqt:final_probability}
  \begin{split}
    \frac{1}{5} \times \frac{1}{9} = \frac{1}{45}
  \end{split}
.\end{equation}

\newpage
