Today, I have decided to follow the \textbf{Uberman Sleep Schedule}.

\begin{mydefinition}[Uberman Sleep Schedule]
  \label{def:uberman_sleep_schedule}

  The practice of taking $20$ minute naps every $4$ hours. So, taking a $20$ 
  minute nap at:
  \begin{itemize}
    \label{item:when_to_take_a_nap}

    \item $12$:$00$ AM
    \item $4$:$00$ AM
    \item $8$:$00$ AM
    \item $12$:$00$ PM
    \item $4$:$00$ PM
    \item $8$:$00$ PM
  \end{itemize}
\end{mydefinition}

There are a ton of things you can do to help reduce the risk of you over
sleeping.
\begin{itemize}
  \label{item:things_that_can_reduce_your_risk_of_over_sleeping}

  \item Control the consumption of sugary food.
  \item Be active.
  \item Don't be in environments that make you want to sleep for too long, or
    you will end of going to sleep, DUH!
\end{itemize}
I've tried this method before, multiple times, but alas, I failed all times.
There was a key element that I was missing, which is something most people
don't like, creating a schedule. The reason this works is because it helps me
see an overview of the entire day, which keeps me motivated to keep going
throughout the entire day. Also, the reason I started this journal writing is
to relax my brain. The reason I relax my brain when writing in this journal is
because I dump all of my ideas that I don't want to forget so I don't have to
walk around all day just keeping track of how many ideas I have. Also,
psychologically helps me as well. Anyway, here's day one:

\subsection*{Day 1}
\label{sub_sec:day_1}

Day $1$ was verily easy, since I slept for almost $13$ hours yesterday. But, I
started out the day just like regular. Woke up at $4$ PM, and just did my
everyday things. I took my first power-nap at $12$ AM. I struggled actually
going to sleep, which is something I will eventually learn, I presume. But, I
just laid there, aimlessly, thinking and regretting about all of my choices in
life. I was afraid that I wouldn't wake up, so I created an entire alarm system
in my house. Fortunately, I woke up without setting off any of the alarms.

% subsection day_1 (end)
