\lesson{6}{Jan 11 2022 Tue (09:23:07)}{Foreign Policy}{Unit 4}

\subsubsection{Domestic vs. Foreign Policy}

\begin{definition}[Domestic Policy]
  \bf{Domestic Policy} is the decision, laws, and programs that address issues
  within a country. It includes laws related to education, such as minimum hours
  of instruction needed per grade, and those related to the environment, like
  the maximum level of emissions allowed for a factory. The lawmaking process in
  Congress determines domestic policy with input from the people, the president,
  and other officials.
\end{definition}

\begin{definition}[Foreign Policy]
  \bf{Foreign Policy} is the decisions and programs a country creates that
  affect relations with other countries.
\end{definition}

\bf{Domestic} and \bf{Foreign Policy} can affect each other. For example, many
foreign policies require funding, and the money needed might come from the
federal budget, which is a domestic policy. Another example is how regulation of
immigration policies can affect relationships with other countries. In the
United States, the goals of foreign policy reflect American values, principles,
and domestic policy.

\subsubsection{Approaching a Foreign Policy}

In a representative democracy like the United States, many people and groups
affect foreign policy, sometimes creating conflict with one another. The U.S.
president has the most influence over foreign policy as he or she is the main
person who meets with foreign officials and leads the military, but the
president cannot act alone. Managing the information and recommendations for
policy change from around the globe is an enormous task. Presidential advisors
in several departments provide information and advice, such as the Secretary of
State who meets with leaders of other countries and the National Security
Advisor. Under the Constitution, the president can send troops into a conflict
and make treaties with other countries. He or she appoints ambassadors and other
federal officials as well.

The Constitution gives Congress certain powers that deal with foreign policy.
Though the president is the leader of the military, only Congress can declare
war. The Senate must approve treaties with foreign countries and presidential
nominations to ambassador and advisory positions. Congress must approve how the
president spends the federal budget.

Conflicts of power between the executive and legislative branches are common in
the area of foreign policy. For example, many presidents have sent troops into a
conflict without prior authorization or a declaration of war from Congress.
Congress passed the War Powers Act in 1973 to place limits on this power.

Yet as long as Congress authorizes more money for a conflict, the president can
continue the military presence. For example, U.S. soldiers remained in Vietnam
for twelve years without a war declaration, from 1961-1975. However, countries
differ in the relative amounts of power between officials in the area of foreign
policy. The British prime minister, for example, can declare war without waiting
for Parliament's approval.

Public opinion and interest groups can complicate foreign policy, with every
side having different interests in its effects. Business owners trading with
those in foreign countries have specific concerns related to trade laws,
tariffs, and maintaining peaceful government relations.

Critics of democracy say that foreign policy is a democratic country's weakest
point, that it is too dependent on the people's will, which compromises
sensitive operations. They say most people have little understanding of foreign
policy, as it does not affect their daily lives. Others note that public opinion
in fact has a positive effect on foreign policy by keeping officials honest and
open about its activities.

\paragraph{Introduction} Each country approaches foreign policy in different
ways and can change it for many reasons. New events might require a change in
approach. Different approaches might be used for different issues or countries,
and they may be used at the same time. The approaches vary in how intensely a
country becomes involved with another. [Image of a spectrum with arrow pointing
to the right stating "Intensity of government action increases."] A spectrum
shows the range of approaches from least interaction, or isolation, on the left.
The other extreme, imperialism, is all the way to the right. Examine each
approach to learn more.

\paragraph{Isolation} Leaders might decide not to work with other countries
other than for trade. We call this approach isolation which is a foreign policy
approach of a country that separates itself from events in other countries. True
isolation would be very difficult to achieve because of the interdependence of
the world's countries. Conflict, natural disaster, and human rights crises in
one country can disrupt trade and create heavy economic consequences for others.
Leaders and the media from around the world may heavily criticize a country that
has the power to help but chooses not to get involved. President George
Washington advised avoiding "entangling alliances" that would surely lead the
country into unnecessary war. The brief periods of isolation in the history of
U.S. foreign policy illustrate how difficult, and undesirable for many, it is to
maintain.

North Korea, as one of the few remaining communist countries, is often described
as one of the most isolated countries in the world. It relies on China for the
vast majority of trade and limits who can enter and leave the country. The
government controls major industries and access to information. Its foreign
policy has focused on building up its military and possible reunification with
South Korea, though tensions between the two and their allies complicate these
plans.

\paragraph{Diplomacy or Internationalism} The foreign policies of most countries
fall between the extremes on this spectrum. Leaders that focus on diplomacy, or
discussion between leaders or representatives from separate nations, talk often
with other world leaders. They wish to address problems before they become
conflicts. Ambassadors are people who work in other countries or international
organizations for diplomacy. The United Nations was formed after World War II,
hoping that through frequent discussions and solving problems together, it could
prevent world war in the future. Organizations based on trade are common as
well, with the purpose of economic agreements to promote peaceful relations and
economic growth for members. The United States has been a founder and active
member in many international organizations. Examples include the Peace Corps and
UN (insert links here). Each organization has a different focus. Peace corp
example here. For example, one may have military alliance focus. Members agree
to help protect each other if one is attacked. Another group may focus on
economic issues and helping developing countries. It could assist countries with
increasing trade and managing their resources.

\paragraph{Interventionism} Sometimes leaders believe they must use military
intervention to deal with a problem. What separates this foreign policy position
from internationalism is the sending of armed troops into a conflict zone,
whether the action does or does not have a direct relationship to domestic
security. The invasions of Afghanistan in 2001 after the September 11th
terrorist attacks and Iraq in 2003 reflected interventionism. Though those
country's governments did not directly sponsor the terrorist attacks, evidence
showed they supported or possibly encouraged them. This is especially the case
concerning the Taliban in Afghanistan, which was known to support the terrorist
organization responsible for that day's attack. The U.S. military was successful
in removing the corrupt leadership from both countries, and efforts to help the
people rebuild the country, both politically and otherwise, continue with U.S.
support.

Acts of intervention often happen in coordination with other countries and
international organizations. The United Nations, for example, has its own
policies for when and how it will send military into a conflict and will request
troops from member countries to support these operations. However, membership in
the United Nations does not stop countries from acting alone. The United States
asked for U.N. support to invade Iraq in 2003 but was denied. With support of
key allies, including Britain, the U.S. military went anyway.

\paragraph{Imperialism} The opposite extreme approach from isolation would be
invading to take over territory from another country, known as imperialism. This
is usually a unilateral attempt, meaning without support from allies, to assert
control over an area not within a country's accepted borders. One example is the
Iraq invasion of Kuwait in 1990, which actually led to the first U.S.
intervention in that country with the goal of protecting Kuwait's independence
(which was successful).

The reasons for imperialism vary but there is typically some specific goal or
aim in mind that benefits the imperialist country, such as access to oil
reserves and seaports in the case of the Kuwait invasion. The United States
tried in the 1960s and early 1970s to prevent North Vietnam, a communist
country, from reunifying with South Vietnam under its communist rule. South
Vietnam was democratic and the United States was trying to "contain" communism,
or keep it from spreading and threatening U.S. interests. In a powerful example
of the pressures of public opinion, that effort was not a success, as American
support for it fell and other problems mounted. Vietnam is one of the few
remaining communist countries today.

\subsubsection{Examples of Foreign Policy Influence}


A key difference between foreign and domestic policy is the timing. Foreign
policy decisions often are more time-sensitive or about an urgent matter that
needs to be addressed. This is why people debate the relative roles of the
executive and legislative branches in making foreign policy. The president often
cannot wait for Congress to make a decision on an issue before taking action.

In the following activity, imagine you are the U.S. president facing each
situation. Select the course of action you would take and see how it compares to
the choices of real U.S. presidents.

\subsubsection{Human Rights}


The idea of rights belonging to humans through God or nature originated during
the Enlightenment and was indoctrinated in the founding documents of the United
States. Many other countries have since established basic rights for citizens in
their own legal documents and policies. The concept of universal human rights,
or rights belonging to all people everywhere and transcending borders and
governments, is relatively new.

\subsubsection{Examples of Human Rights Policy}

Creation of the Universal Declaration of Human Rights, like the U.S. Bill of
Rights, is just a start and not an end to human rights policy. Enforcement of
the rights requires a collection of interlocking agreements, treaties, and
domestic policies. The United Nations creates sanctions for countries that fail
to abide by its agreements, but that is not always enough to stop human rights
abuses, nor is political pressure from various countries always effective.
Unfortunately, human rights issues are constant around the world, though some
are resolved through diplomacy or intervention. While most of the world's
countries participate to some extent in the international community, leaders
often resent attempts of other countries to interfere with what they may
consider solely a domestic issue.

\newpage
