\lesson{5}{Jan 10 2022 Mon (18:24:27)}{Comparing Governments}{Unit 4}

\subsubsection{Types of Governments}

The country's constitution, laws, and traditions play a big role when organizing
the basic structure of its government. But, it doesn't all last. For example, a
war could lead to a brand new constitution. New laws, change in leadership, and
conflicts can lead to a different government structure. When new people come to
power with new ideas, they will create laws that may change the way the
government works.

The terms we use to describe styles of government can apply to multiple
countries, with no two countries having exactly the same features.

The three main types of government differ in how much power the people have in
making decisions:

\begin{itemize}
  \item democracy
  \item oligarchy
  \item autocracy
\end{itemize}

Governments also differ in how they manage their political divisions, such as
state or local governments. Some of the arrangements are:

\begin{itemize}
  \item unitary
  \item confederation
  \item federation
  \item parliamentary
\end{itemize}

\subsubsection{Best Government}

A country's leaderships considers many factors, including geography, resources,
and culture when trying to determine the most suitable form of government.

Countries can change their form of government, with new policies that shift
power structures over time. Countries with autocratic or oligarchic rule have
made reforms toward democracy in the last few generations, a process called
democratization.

\begin{definition}[Representative Democracy]
  A government that is elected by citizens.

  \paragraph{Advantages} Citizens have an active role in making decisions. They
  elect their leaders. The leaders know that they must meet people's needs to
  stay in office. Leaders who do not represent voters well will not win
  re-election. In some places, voters could take them out of office early!

  \paragraph{Disadvantages} Making decisions is very time consuming. It is
  difficult to get the majority of elected leaders to agree on decisions.
  Leaders do not always make decisions that satisfy the voters.
\end{definition}

\begin{definition}[Oligarchy]
  A government which is ruled by a small group who are in complete control.

  \paragraph{Advantages} Decisions can be made quickly. The leaders of an
  oligarchy usually share similar views, so it is easy to agree on decisions.

  \paragraph{Disadvantages} Oligarchies often must use force to stay in power.
  The leaders may not consider the people's wishes when making decisions.
\end{definition}

\begin{definition}[Autocracy]
  A government with one person in absolute power.

  \paragraph{Advantages} Decisions can be made quickly since the ruler does not
  need to consult others.	

  \paragraph{Disadvantages} Leaders of autocracies have often ignored the
  people's needs and wants. He or she can make decisions for his or her own
  benefit. Decisions can be very poor since no one is consulted. Basic civil
  rights of the people usually do not exist or are not protected.
\end{definition}

\begin{definition}[Unitary]
  A government of political organization where most or all of the governing
  power is in a centralized government.

  \paragraph{Advantages} The same rules, policies, laws, and standards are the
  same throughout the nation. There is less overlap of services and therefore
  less chance of wasting tax dollars and government resources. The nation has
  greater unity and fewer conflicts between different levels of government.

  \paragraph{Disadvantages} The central government may not be aware of issues in
  local areas and therefore may be slow to do anything about them. On the other
  hand, if the government is too involved in local concerns, it can neglect
  people in other areas or issues of national concern.
\end{definition}

\begin{definition}[Federation]
  A government formed by separate states that have given certain powers to a
  central government while keeping control over local matters.

  \paragraph{Advantages} It has unity as one nation but local governments
  address local concerns. Central government can focus on national issues and
  relationships with other nations. Citizens have opportunity to participate at
  multiple levels.

  \paragraph{Disadvantages} Government services may overlap at different levels.
  This can be inefficient and lead to waste or service failure, especially in a
  crisis. There may be conflict and power struggles between different levels of
  government.
\end{definition}

\begin{definition}[Confederation]
  A government confined to a permanent union of sovereign states for a certain
  common purpose.

  \paragraph{Advantages} Power is focused at the local levels of government. It
  prevents abuse of power by a large, central government. Members of a
  confederation can keep their laws and identities while cooperating with others
  on shared concerns.

  \paragraph{Disadvantages} Central government may be too weak to be effective.
  There is little to no unity or common laws across members.
\end{definition}

\subsubsection{Measure Democracy}

We can use many different types of data to evaluate the democratic nature of a
country's government. For example, many people relate a higher gross domestic
product (GDP) with greater levels of democracy. However, it is important to look
at many pieces of data, both qualitative and quantitative. No study has proven
that one data type perfectly correlates with a country's level of democracy. We
must study different characteristics of a government, as well as statistics, to
make a fair judgment.

In addition, a single number can be misleading because countries vary a great
deal in size and population. Data "per capita" gives a better idea of daily
life. Analysts label many pieces of data, such as GDP as "per capita" or "rate"
to show the data by each person or a certain number of people.

Here are some indicators for a democracy government:

\begin{enumerate}
  \item GDP \\
  \item Internet Users \\
  \item Education and Literacy Rate \\
  \item Economy and Natural Resources \\
  \item Culture, Population, and Elections \\
  \item Freedom House \\
\end{enumerate}

\subsubsection{Democratization Taking Place}

Democratization is the name for a process where a country changes to a more
democratic government. History is full of examples of such changes, such as U.S.
independence and the transitions in Europe from powerful monarchies to
republics. Freedom House reported that between 1972 and 2005, dictatorships fell
in 67 countries. Some places noted for changes toward increased democracy in the
twenty-first century include Hong Kong and Myanmar. However, democratization is
not always a matter of constant progress or a linear process. It can, and has,
faced setbacks in many places and times.

Hong Kong, once a colony of Britain, is a special administrative district of
China and has greater sovereignty than other parts of the country. Its market
economy is much freer of economic control than mainland China. The people have
been debating whether to implement reforms that would increase democracy, such
as universal suffrage and increasing the number of representatives in the
district's government. Yet Hong Kong has had large protests in recent years,
reflecting its people’s lack of approval for the degree of progress in
democratic reform. A new law in 2020 puts restrictions on free speech and casts
doubt over the future of democratization in Hong Kong.

From 1962 until 2010, Burma, now the Republic of the Union of Myanmar, was under
military control. Since 2008, the country has enacted democratic reforms, while
receiving heavy foreign criticism for accusations of fraudulent elections,
police violence, and corruption. Pro-democracy leader Aung San Suu Kyi was
released from house arrest in late 2010, allowing her to freely travel the
country and continue activities that support reform. In 2016, Suu Kyi was even
elected to serve in executive positions. However, in that time Suu Kyi has also
faced international criticism for her leadership, such as inaction in the
genocide of the Rohingya people. As a result of the contested 2020 election,
there was a military coup d’etat in early 2021. The military resumed control of
Myanmar and placed Suu Kyi and the nation’s president under house arrest.

\subsubsection{Government's Affect on Resource Use}

The degree to which government controls natural resources may be an indicator of
the extent of democratic reforms occurring within a country. Many countries are
lucky to have plenty of natural resources and arable land. From oil to fuel,
agricultural or mining machines, and land to grow corn, the United States is
rich in resources. Finding more uses for a natural resource increases its value.
For example, corn has many uses besides food. Ingredients made from corn are
important to producing paints, paper, stamps, tape, and medicines. Because the
United States is rich in natural resources, it has many products it can sell and
trade. Countries that lack natural resources can stimulate their economy in
other ways, such as providing services. Services include web design,
restaurants, hotels, and cleaning companies. Islands in the Caribbean, such as
the Bahamas, export few types of food yet the tropical climate and short
distance to the United States have created a booming tourist industry.

Other countries have resources the United States does not. For example, bananas
are popular among Americans but are difficult to grow in most parts of the
United States. The U.S. imports, or brings in, a majority of bananas from other
countries. The United States exports products to countries on every continent.
Even in a free society, the government can play a key role in how the people use
and manage resources, including rules for import and export. It might lower
taxes on certain industries to encourage people to increase production in those
areas. It sets regulations to increase consumer and worker safety as well as
protect the environment. A country could ban goods produced in certain countries
deemed inferior or produced in an unacceptable manner. A recent example is the
public awareness campaign of violence and child soldiers in Africa, linked in
part to trade in illegal diamonds. International organizations have created
policies aimed at preventing profits from illegal trade from going to groups
that spread more violence and discourage democracy.

\subsubsection{Examples of Resource Management}

After World War II, resource use and management grew into an important political
issue in countries around the world, especially in industrialized countries
heavily dependent on natural resources such as oil. Environmental concerns grew
as people discovered the negative impacts of pollution. Most governments have
policies related to production and consumption of various national resources, as
well as imported resources. They often encourage expansion of renewable
resources.

Governments have also come together through international organizations to
cooperate in these efforts and protect Earth and its resources for future
generations. Participation in these initiatives varies, with some countries
resistant to rules imposed by outside groups or rules that seem unfair, given
their own political or economic conditions. A crisis can have a great impact on
these initiatives and their application around the world.

\paragraph{Waste} All living things produce waste through their daily
activities, with people in industrialized countries being some of the worst
offenders due to use of plastics and chemicals that are not easily recycled.
Factories produce great amounts of waste that can find their way to waterways
and pollute both air and water. Efforts to reduce waste and use renewable
resources exist everywhere, from small communities to international
organizations.

The American public was increasingly concerned about the environment and waste
in the 1960s and 1970s. President Richard Nixon established the Environmental
Protection Agency in 1970 to address the concerns. Congress has created
legislation that businesses must follow to reduce pollution and waste. The EPA
is in charge of regulating and enforcing those laws. For example, the EPA sets
limits for gas waste that a factory can release into the air. It has rules about
how businesses should handle all types of waste, such as preventing chemicals
from draining into rivers.

\paragraph{Oil} The cost of oil and its products is a top issue in many
countries, as they depend on it for their main source of fuel in a wide variety
of human activity. In 1960, representatives from five oil-rich countries met in
Baghdad, Iraq and created the OPEC organization, or the Organization of
Petroleum Exporting Countries. OPEC coordinates policies on petroleum in its
member countries, with the mission of keeping prices and supply stable for
consumers around the world. Examples include maximums for amounts of oil drilled
in a given timeframe and minimum prices for a barrel of crude oil. Some people,
including many in the United States, have a negative view of OPEC as unfairly
controlling oil prices and access in a way that benefits themselves or political
allies. They think the natural forces of supply and demand should control prices
and supply, a value common to democratic countries with market economies. In the
United States alone there are over 300 oil refineries. Refineries break down oil
into parts to create the products used in homes and businesses each day, such as
motor oil, kerosene, petroleum, and gasoline.

\paragraph{Emissions} Emissions are the gases released into the air from fuel
consumption such as that of gasoline-burning engines. They are a global concern
because of scientific analysis that Earth's climate is undergoing change and
humans are part of the problem.

The Paris Agreement was signed by the majority of the world’s nations in 2016.
It is intended to replace the Kyoto Protocol; like this earlier pact, the Paris
Agreement is a commitment to reduce emissions as quickly as possible. Each
participant nation agrees to find ways through its own laws and regulations to
reduce pollutants from factories and consumers. Both the Paris Agreement and its
predecessor have been controversial in the United States. This is because
increasing regulations is often costly for government, businesses, and
individuals. However, the United States has made significant strides in reducing
emissions since passage of its Clean Air Act of 1970.

\newpage

