Apocalypse is \textit{"an event involving destruction or damage on an awesome or
catastrophic scale" (Google)}. A question that I had in mind while reading this
book was: \textbf{Does this story qualify as an apocalypse?} Yes, this story is
an exceptional example of an apocalyptic event. It shows the destruction of
multiple things and the rebirth of them. It shows the de-composition of the
Lager, humans transforming into the lowest of creatures worms, the end of
countless lives, and the re-birth of a lucky, selected few.

In the beginning of the chapter, Primo says \textit{"\ldots I was lucky enough
to have a bunk entirely to myself \ldots"} That is an exceedingly common phrase
throughout the book.

In the middle of the story \textbf{The Story of Ten Days}, Primo describes the
Lager as \textit{"The Lager, hardly dead, had already begun to decompose \ldots"
(Pg. $158$)} Eventually, in the story, we see that the decomposition of the camp
is essential in creating a new world for Primo and the people with him.
\textit{"The work of the bombs had been completed by the work of man \ldots (Pg.
$158$)"} This statement, appears to be criticising or telling that man is
responsible for the destruction of their own kind. Then Primo goes on to
describe the people who are suffering in the camp. \textit{"\ldots ragged,
decrepit, skeleton- like patients at all able to move dragged themselves
everywhere on the frozen soil, like an invasion of worms \ldots (Pg. $158$)"}
Here, Primo is comparing the people who are suffering in the camps to worms.
This may indicate that he's telling us that the Lager has transformed the people
into the lowest of life form, worms. \textit{"no longer in control of their own
bowels, they had fouled everywhere, polluting the precious snow, the only source
of water remaining in the whole camp \ldots" (Pg. $158$)} Primo describes the
suffering people with disgust, but when he mentions the snow, he elevates its
status by calling precious, which indicates that the snow, to him, is more
valuable than those people. Without the snow, he wouldn't have any water to
drink and those people keep depleting the amount of water they have.

The remaining patients in the Lager have formed a somewhat sense of a community.
\textit{"\ldots by now a tie united us, the eleven patients of the
Infektionsabteilung \ldots" (Pg. $160$)} This shows the importance of a
community. 

\textit{"Very occasionally we heard the thundering of artillery, bot near and
far, and at intervals the crackling of automatic rifles. In the darkness,
lighted only by the glow of the embers, Arthur and I sat smoking cigarettes made
of herbs found in the kitchen and spoke of many things, both past and future. In
the middle of this endless plain, frozen and full of war, in the small dark room
swarming with germs, we felt at peace with ourselves and with the world. We were
broken by tiredness, but we seemed to have finally accomplished something useful
-- perhaps like God after the first day of creation." (Pg. $161$)}

I think this passage is the most beautifully written passage throughout the
entire story. I believe that this part is what changed him. It seems that Primo
and Arthur have grown close together and when they were chatting, perhaps it
struck something inside of them that made them want to overcome all the
obstacles that they are facing, which ended up giving them peace.
When Primo says that they have finally accomplished something useful, perhaps
he's refereeing to all of the stuff that they have done up until that point,
which are stuff like how they found the stove and got potatoes. I do find it odd
how he compares that feeling to the feeling of "God after the first day of
creation".

A couple of pages after this passage, Primo starts to gather all of the
remaining patients and encourage them to want to overcome the struggles.
\textit{"I was thinking life outside was beautiful and would be beautiful again,
and that it would really be a pity to let ourselves be overcome now. I woke up
the patients who were dozing and when I was sure that they were all listening
I told them, first in French and then in my best German, that they must all
begin to think of returning home now, and that as far as depended on us,
certain things were to be done and others to be avoided \ldots" (Pg. $164$)}
Here, he realizes how beautiful life is and he doesn't want to end his life just
then. He then starts to instruct the remaining patients on what to do and not to
do. \textit{"Each person should carefully look after his own bowl and
spoon; no one should offer his own soup to others; no one should climb down
from his bed except to go to the latrine; if anyone was in need of anything,
he should only turn to us three. Arthur in particular was given the task of
supervising the discipline and hygiene, and was to remember that it was
better to leave bowls and spoons dirty rather than wash them with the danger
of changing those of a diphtheria patient with those of someone suffering from
typhus." (Pg. $165$)} Something struck Primo deeply for him to start this
somewhat survival plan. But, what he's really doing is creating a community,
where everyone looks out for each other. He puts the people who are not as sick
to help and protect, if needed the tribally ill, which ended up working because,
at the end of the story, Primo says \textit{"Of the eleven of the
Infektionsabteilung Somogyi was the only one to die in the ten days \ldots" (Pg.
$173$)}

At the end, Primo says \textit{"\ldots Sertelet, Cagnolati, Towarowski, Lakmaker
and Dorget \ldots died some weeks later in the temporary Russian hospital at
Auschwitz. In April, at Katowice, I met Schneck and Alcalai in good health.
Arthur has reached his family happily and Charles has taken up his teacher's
profession again; we have exchanged long letters and I hope to see him again one
day." (Pg. $173$)} The ending seems to be sad, which I wasn't expecting. I hoped
that they would all survive and they would have a life long friendship, but
about half of the survivors end up dying, and the rest just split up. But, the
survivors most likely had their life changed for the better and they now see
what is really important in life.
