The bombing of Hiroshima is unacceptable! Hundreds of thousands of people lost
their lives, so much destruction happened, and it didn’t just affect Hiroshima.
It also affected the US. The nightmare began on August 6, 1945 at 8:15,
according to the survivors. Hundreds of thousands of people were going work,
going to school, sleeping, having breakfast, etc. Then, there was the silent
big, burning, flash, which occured at 8:15 AM. Nobody knew what was going on.
All they felt was a tremendous burn. Some even lost their facial skin. After the
big flash left, most thought it was over. Unfortunately, it was only the
beginning.

If you were there to witness the horror, trauma, pain, and suffering of those
people, you would be scared for life! \it{"All his hand skin was hanging over
his fingers."} This quote is from one of the survivors. He was only 16 years old
when he witnessed what happened to his cousin. His cousin’s skin on his fingers
was all down dang lining in front of his nails, his face has full of blood, and
he was barely awake. \it{"...roughly 136, 000 people are living with the
memories—and effects—of the disasters. In the U.S., specifically, there are
believed to be just under 1, 000 survivors. Many of these men and women ended up
in Hiroshima and Nagasaki as children or young adults on those fateful days
because they were visiting extended family, or had been sent to study in the
country during a time of rising anti-Asian sentiments in the U.S" Hundreds of
thousands of people are affected mentally and physically by this bombing."}

The affect of bomb didn’t just stop in Hiroshima, it spread around
the world. \it{"Other Americans were troubled by casualty reports that placed the
fatalities from the bomb at 100, 000 ..."} Even Americans were troubled by the
bombing of Hiroshima. \it{"When Americans learned in August 1945 that the atomic
bomb had been dropped on Japan, they reacted with a variety of complex and
sometimes contradictory responses – awe, fear, satisfaction, hope, uncertainty,
and bewilderment. Despite their confusion about the military and peacetime
implications of atomic energy, however, Americans reached near agreement on
one point: they approved the atomic bombings of Hiroshima and Nagasaki. A
vocal minority regarded the atomic attacks on two urban centers as atrocities,
comparable to the Nazi extermination camps."} The bombing even started to
create different groups, ones who believed in the bombing, and one group that
regarded the bombing like the concentration camps. And we all know how
terrible the concentration camps where, and if someone starts to say it was like
that, then it was series.

You might be familiar with the German Concentration Camps because a whole World
War was based around it. But, a lot of people may not be educated about the
bombing of Hiroshima. Well, now you’re going to find out some of the stories
during the bombing. \it{"Some were naked, their clothes burnt off them. They
walked along with their arms raised and something hanging off them that looked
like nylon stockings. It was their burnt flesh peeling away. They were
disintegrating."} When you continue to read facts and stories that happened
during the bombing and compare it to this, this is nothing. Some people where
literally betting their skin, muscle, and all of their systems burned, some lost
their limbs and just bled to death, and the least worst was someone dying from
suffocation or a building collapsed on them.

\it{"When I came to again, I was covered by debris. All I could see was a broken
ceiling and through it, the grey sky. I assumed a bomb had fallen directly on
our house. In my mind, I heard tens of thousands of people in Hiroshima
screaming. I don’t know if that’s true, but it’s what I remember. My sister and
I were clinging to each other. We tried to crawl out. To make sure we were all
right, we siblings were calling to each other: “Junko-chan!” “Tei-chan!”
“Aki-chan!” “Where are you? We’re here.” I found my eldest sister in what was
left of the dining room. She was covered in blood. I wondered why there was all
that blood over her. She was hurt, and one of her teeth was missing. The shock
had sent one of the chopsticks she was holding through her cheek, poking out the
tooth. Our brother was in another room. The window behind him had shattered.
When the window broke with a bang, his back was pierced by splinters of
shattered glass. We heard the noise fade. Suddenly there was a moment of
blinding light with intense heat. I couldn’t see anything. There was a strange
reverberation, a noise that’s impossible to describe, followed by a bang. Then
the house, the ceiling, everything collapsed. We were buried and in complete
darkness. That’s when I thought “I’m going to die”. I repeated to myself, “I’m
going to die, I’m going to die”. The third time I said it, I must have lost
consciousness." This is just what one person went through. Her entire family
where destroyed, their house, gone, and their health, down the drain. Just
imagine how terrible it could have been and how it was for people closer to the
bomb. Some people where burning for almost 10 minutes straight. Some, they bled
to death because of loosing their limbs, etc.}

In conclusion, we will never be able to fully understand and feel what the
residents of Hiroshima felt during the incident. What’s in the past is in the
past and let’s just move on. But, if watch interviews of the survivors, the
majority say that it felt like a big nightmare and some cannot even believe that
it happened.

