\section{Part 1: Background Information}

%%%%%%%%%%%%%%%%%
% Question 1.1
%%%%%%%%%%%%%%%%%

\paragraph{1.1} According to the background information, how many recognized
tribes exist in Oregon today?

\bf{Today, there are $9$ federally recognized tribes with reservation lands
    in \it{Oregon}.}

%%%%%%%%%%%%%%%%%
% Question 1.2
%%%%%%%%%%%%%%%%%

\paragraph{1.2} How would you define time immemorial?

\begin{definition}[Time Immemorial]
  As a point in time that’s so long ago that no one has any knowledge or memory
  of it and no documents or anything of that matter to tell exactly when it was.
\end{definition}

%%%%%%%%%%%%%%%%%
% Question 1.3
%%%%%%%%%%%%%%%%%

\paragraph{1.3} How would you define sovereignty?

\begin{definition}[Sovereignty]
  Having absolute power.
\end{definition}

%%%%%%%%%%%%%%%%%
% Question 1.4
%%%%%%%%%%%%%%%%%

\paragraph{1.4} Using this \href{https://native-land.ca/}{link}, research which tribes have historically occupied the land
where you live:

\bf{The \it{Tualatins} or the \it{Atfalati} used to live in \it{Portland, Oregon}.}

\newpage

\subsection{Part 2: Anatomy of a Supreme Court Decision}

%%%%%%%%%%%%%%%%%
% Question 2.1
%%%%%%%%%%%%%%%%%

\paragraph{2.1} What do you KNOW about Supreme Court decisions?

\bf{I don't know much. I do know for sure that no lower court can oversay the
supreme court. The supreme court is like the president for courting.}

%%%%%%%%%%%%%%%%%
% Question 2.2
%%%%%%%%%%%%%%%%%

\paragraph{2.2} What do you WANT to know about Supreme Court decisions?

\bf{I want to know exactly what happenes. Not just the basics like what the
justices do, what they say, the different opinions, etc. I want to know exactly
how the issue rises to the supreme court, how it's handled and how the judge
respondes.}

%%%%%%%%%%%%%%%%%
% Question 2.3
%%%%%%%%%%%%%%%%%

\paragraph{2.3} List one of the ways that a case can get to the Supreme Court

\bf{Here are four ways a case can reach the supreme court:}

\begin{itemize}
  \item Someone writes a certiorari
  \item An appeal
  \item The solicitor General
  \item Selecting Cases.
\end{itemize}

%%%%%%%%%%%%%%%%%
% Question 2.4
%%%%%%%%%%%%%%%%%

\paragraph{2.4} What is the purpose of a syllabus in a Supreme Court Opinion?

\bf{It’s to help the reader better understand the case and the decision.}

%%%%%%%%%%%%%%%%%
% Question 2.5
%%%%%%%%%%%%%%%%%

\paragraph{2.5} When reading a Supreme Court Opinion, what are the "big picture"
takeaways that you should focus on?

\bf{I think the key takeaways that you should focus on are the reasoning behind
the decision. Like, instead of just only learning the decision that was made,
you should you learn why it was made and how it was made.}

\newpage

\subsection{Part 3: The Supreme Court’s Impact on Native Americans on Oregon}

%%%%%%%%%%%%%%%%%
% Question 3.1 %%
%%%%%%%%%%%%%%%%%

\paragraph{3.1} What was the date of this decision?

\bf{The date of the decision was: \it{April} $17$, $1990$}

%%%%%%%%%%%%%%%%%
% Question 3.2 %%
%%%%%%%%%%%%%%%%%

\paragraph{3.2} What is the summary of the case? (What was this case about?)

\bf{This case was about if a state can refuse un-employment benefits
to workers fired for using illegal drugs for religious purposes.}

%%%%%%%%%%%%%%%%%
% Question 3.3 %%
%%%%%%%%%%%%%%%%%

\paragraph{3.3} Who gave the majority opinion? What did he say?

\bf{\it{Antonin Scalia} gave the majority opinion. He stated that an
individual’s religious beliefs do not excuse them from complying with the law.
And I agree with him. For example, if someone's religion told them to sacrifice
someone random, and you go do it, your excuse shouldn't be "my religion told
me". So, he does have a point.}

%%%%%%%%%%%%%%%%%
% Question 3.4 %%
%%%%%%%%%%%%%%%%%

\paragraph{3.4} Who gave the dissenting opinion? What did they say?

\bf{\it{Harry Blackmun} gave the dissenting opion. He stated that the state law
banning peyote possession didn't server as a compelling state interest.}

%%%%%%%%%%%%%%%%%
% Question 3.5 %%
%%%%%%%%%%%%%%%%%

\paragraph{3.5} How did this decision impact tribes in Oregon?

\bf{Before, the tribes were able to do whatever they want and say the excuse,
their religion told me to do so. Now, they have rules and regulations that they
must follow to limit the stupidity of people.}

\newpage

\subsection{Part 4: The Supreme Court’s Impact on Native Americans in Oregon}

%%%%%%%%%%%%%%%%%
% Question 4.1 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.1} What was the date of this decision?

\bf{The date of the decision for the case \bf{Oregon Department of Fish \&
    Wildlife v. Klamath Indian Tribe} was on July, $2$, $1985$}

%%%%%%%%%%%%%%%%%
% Question 4.2 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.2} What is the summary of the case? (What was this case about?)

\bf{In $1864$, the \it{Klamath Tribe} signed a treaty with the government, which
    ceded most of the land in the \it{Klamath Indian Tribe} to the government for
    federal protection, a designated reservation for the tribe, and exclusive rights
    for the tribe to hunt and fish on the reservation. The right to hunt and fish on
    the tribe’s ancestral territory that lay outside the reservation was not clearly
    defined in the treaty, however. After a dispute between the government and the
    tribe, the government negotiated the $1901$ Cession Agreement, which congress
    ratified.}

\bf{But, from the agreement, the tribe gave all of their land to the government
    without any rights to hunt and fish outside of the reservation. But, the
    tribe kept on hunting and fishing on the ceded land.}

\bf{In $1982$, the tribe brought this case against the \it{Oregon Department of
    Fish and Wildlife} to prevent the government from interfering with their
    tribal hunting and fishing. On \it{July $2$, $1986$}, a $6:2$ vote ended
    stating that the tribe didn't have the exclusive right to hunt and fish on
    tribal lands that were ceded in the $1864$ treaty. They also ruled that the
    tribe was not free of state regulation on ceded lands that were outside of
    their reservation.}

%%%%%%%%%%%%%%%%%
% Question 4.3 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.3} Why did the tribe bring this case to court?

\bf{The tribe brought this case to court because they felt like they were
    cheated out of their rights. They didn't know that if they signed the treaty of
    $1901$ that they would loose all of their rights to hunt and fish on the ceded
    lands.}

%%%%%%%%%%%%%%%%%
% Question 4.4 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.4} Who gave the majority opinion? What did he say?

\bf{\it{John Paul Stevens} gave the majority opinion.
    He stated that the $1864$ treaty restricted the tribe's hunting and fishing
    on the reservation. Since there was no mention of off-reservation hunting
    and fishing rights in the $1901$ Cession Agreement, that didn't mean these
    rights were granted. From that, the tribe was not given the permission to hunt
    and fish on the ceded lands.}

%%%%%%%%%%%%%%%%%
% Question 4.5 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.5} Who gave the dissenting opinion? What did they say?

\bf{\it{Thurgood Marshall} gave the dissenting opinion.
    He stated that the tribe had hunted and fished on those lands for years
    without being interfered with. The Court's decision assumed that the tribe
    had given up their rights to hunt and fish on those lands by signing the
    $1901$ Cession Agreement. According the \it{Marshall}, there isn't any proof
    that any of the two parties that signed the $1901$ agreement predicted that
    there would be an impact on the tribal hunting and fished practices.}

%%%%%%%%%%%%%%%%%
% Question 4.6 %%
%%%%%%%%%%%%%%%%%

\paragraph{4.6} How did this decision impact tribes in Oregon?

\bf{This impacted other tribes in \it{Oregon} because that made them more aware
    of the treaties that they sign and the consequences. Also, this probably
    made other tribes not want to deal with the government because they might
    think that other tribes not want to deal with the government because they
    might think that they will try to cheat them out of their lands.}
