\lesson{4}{Sep 13 2021 Mon (10:54:11)}{Properties of Matter}

There are four known states of matter:

\begin{itemize}
  \item Solid
  \item Liquid
  \item Gas
  \item Plasma
\end{itemize}

\begin{definition}[Phase]
  Each one of these stages is known as a \textbf{Phase}. Each one has it's own properties, such as:

  \begin{itemize}
    \item Shape
    \item Particle Motion
  \end{itemize}
\end{definition}

\textbf{Solid substances} can be \textbf{hard}, or \textbf{soft}, but they have
low \textbf{compressibility} and usually maintain their shape on their own.

On the other hand, a substance in a \textbf{liquid} will take the shape of the
container it's poured into and fill the container from the \textbf{bottom up}.

A \textbf{gas substance} will fill up the entire container spreading out evenly
because their particles can be forced closer together with pressure.

Like \textbf{gas}, \textbf{plasma} can spread evenly in a container and be
compressed, but its composition differs. \textbf{Plasma Particles} are
positively and negatively charged, which allows plasma to conduct electricity
and create magnetic fields.

A \textbf{physical property} can be changed without altering the identity of a
material. Each physical properties can be classified as either an
\textbf{Extensive Property}, or an
\textbf{Intensive Property}.

\subsection*{Extensive Property}
\label{sub_sec:extensive_property}

\begin{itemize}
  \item Shape
  \item Volume
  \item Length
  \item Mass
\end{itemize}

are classified as \textbf{Extensive Physical Properties}. An extensive property
is a physical property that depends on the sample size.

\begin{example}[Extensive Physical Properties]
  For example, if you have a large amount of metal and a small amount of the same
  metal, these two samples will have different volumes.
\end{example}

% subsection extensive_property (end)

\subsection*{Intensive Property}
\label{sub_sec:intensive_property}

\begin{itemize}
  \item Magnetism
  \item Density
  \item Melting
  \item Boiling
  \item Points
  \item Color
\end{itemize}

are all classified as \textbf{Intensive Physical Properties}. Intensive
properties do not depend on the size of the samples. No matter how much or how
little of the substance you have, an intensive physical property stays the
same.

\begin{example}[Intensive Property]
  For example, if you have a large amount of metal and a small amount of
  the same metal, these two samples will have the same density.
\end{example}

% subsection intensive_property (end)

\subsection*{Physical Properties of Matter}
\label{sub_sec:physical_properties_of_matter}

\begin{definition}[Phase State]
  The phase:

  \begin{itemize}
    \item Solid
    \item Liquid
    \item Gas
    \item Plasma
  \end{itemize}

  of a substance is a physical property.
\end{definition}

\begin{definition}[Density]
  The ratio of mass per volume is a physical property that does not depend on
  the size of the sample.
\end{definition}

\begin{definition}[Ductility]
  The ability to be pulled or stretched to make wire is a physical property of
  metals.
\end{definition}

\begin{definition}[Malleability]
  Some substances have the ability to be:
  \begin{itemize}
    \item shaped
    \item Dented
    \item Extended
  \end{itemize}

  by beating with a:
  \begin{itemize}
    \item Hammer
    \item Rolling
  \end{itemize}
\end{definition}

\begin{definition}[Melting Point]
  The temperature at which a solid becomes a liquid is its \textbf{Melting Point}.
\end{definition}

\begin{definition}[Solubility]
  A substance is \textbf{Soluble} if it's able to dissolve in another substance.
\end{definition}

\begin{definition}[Boiling Point]
  The temperature at which a liquid becomes a gas is its \textbf{Boiling Point}.
\end{definition}

\begin{definition}[Compressibility]
  \textbf{Compressibility} is a physical property. It describes how much the
  volume of matter decreases under pressure. Substances with high
  compressibility can be squeezed or flattened to fit into smaller spaces.
\end{definition}

\begin{definition}[Electrical and Thermal Conductivity]
  The ability to transmit electricity or heat through the structure of a
  substance is a physical property shared by all metals.
\end{definition}

% subsection physical_properties_of_matter (end)

\subsection*{Density}
\label{sub_sec:density}

Because density is an intensive physical property, its value for a substance
does not change based on the sample size of that substance. Because of this,
density is often used to identify unknown materials. Density measures the
degree to which something is compacted, or the quantity of mass per unit
volume.

\[
  density = \frac{mass}{volume}
.\] 

\begin{example}[Example One]
  The sample of a cork has a mass of $2.88 g$ and a volume of $12.0 mL$. What's the density of the cork?

  We have the following information:

  \begin{align*}
    mass = 2.88 g \\
    volume = 12.0 mL
  .\end{align*}

  We are asked to calculate density. So, use the formula:

  \[
    density = \frac{mass}{volume}
  .\]

  Substitute the numbers and divide:

  \begin{align*}
    d = \frac{2.88 g}{12.0 mL} \\
    d = 0.25 \frac{g}{mL}
  .\end{align*}
\end{example}

\begin{example}[Example Two]
  This sample of marble block is in the shape of a \textbf{cube}. It has a mass
  of $22.4 kg$ and a side length of $2 m$. What's the density of the block?

  First, find the volume of the cube:

  \begin{align*}
    V = (2 m)^3 \\
    v = 8 m^3
  .\end{align*}

  The given information:

  \begin{align*}
    mass = 22.4 kg \\
    volume = 8 m^3
  .\end{align*}

  So, use the formula:

  \begin{align*}
    density = mass/volume
  .\end{align*}

  Substitute the numbers and divide:

  \begin{align*}
    d = \frac{22.4 kg}{8 m^3} \\
    d = 2.8 \frac{kg}{m^3}
  .\end{align*}
\end{example}

% subsection density (end)

\subsection*{Chemical Properties of Matter}
\label{sub_sec:chemical_properties_of_matter}

\begin{definition}[Reactivity]
  \textbf{Reactivity} is a chemical property. It refers to the readiness of a substance to undergo a chemical change.

  There are some substances, like gold or platinum, that do not react so easily
  with other substances. The low reactivity of these elements is perfect for
  jewelry making because they will not rust or tarnish when exposed to other
  substances.

  An element with high reactivity, like fluorine - a poisonous gas - can spontaneously explode when exposed to other substances.
\end{definition}

\begin{definition}[Flammability]
  \textbf{Flammability} is a chemical property. It describes how easily a
  substance can be set on fire. This is very important when it comes to
  building safety.

  For instance, some Styrofoam-based insulation products have higher
  flammability than other fire-resistant products. Builders avoid using
  flammable materials in homes.

  Alcohol and gasoline are two liquids that are highly flammable.
\end{definition}

\begin{definition}[Toxicity]
  \textbf{Toxicity} is a chemical property. It describes the ability of a
  substance to damage or harm an organism.

  Higher toxicity equals more harm. For example, exposure to a gram of mercury,
  an element that is liquid metal, can cause death to humans.
  
  There are some creatures that are labeled venomous or poisonous because of
  their ability to harm other living creatures due to the toxic substances they
  naturally produce.
\end{definition}

\begin{definition}[Heat of Combustion]
  The \textbf{heat of combustion} is a chemical property. It measures how much
  heat is given off when a substance is burned.
\end{definition}

\begin{definition}[Corrosion]
  \textbf{Corrosion} is the irreversible damage or destruction of a material
  due to a chemical or electrochemical reaction.
\end{definition}

\begin{definition}[Decomposition]
  Some compounds decompose into more than one different element or compound as
  bonds are broken. Hydrogen peroxide ($H_2O_2$), a chemical you may have
  around your house, is stored in a dark container to slow down
  \textbf{decomposition}, which can be caused by heat and light.
\end{definition}

% subsection chemical_properties_of_matter (end)

\newpage
