\subsection{Review Questions}

\begin{enumerate}
  \item What is logistics?
      \begin{definition}[Logistics]
        It's the overall process of managing how resources are collected, stored,
        and transported to their final destination.
      \end{definition}
  \item How do agents, wholesalers, and retailers differ?
      \paragraph{Agents:} An individual who manages another person's company, or a
        group's business affairs.
      \paragraph{Wholesalers:} An individual or a company who sells goods in large
        amounts at low prices. The majority of the time, he/she are selling them to
        retailers.
      \paragraph{Retailers:} A person or business that sells goods to the public
      in small amounts for usage/consumption.
  \item What is a promotional mix?
      \begin{definition}[Promotional Mix]
        It refers to one of the marketing mix's 4Ps:
        \begin{enumerate}
          \item Advertising
          \item Public Relations
          \item Personal Selling
          \item Sales Promotion
        \end{enumerate}
      \end{definition}
  \item What is the difference between a direct distribution channel and an
    indirect distribution channel?
      \paragraph{Direct Distribution:} A direct sale between the manufacturer
        and the consumer
      \paragraph{Indirect Distribution:} A manufacturer uses a wholesaler or
        retailer to sell their products
  \item What activities are involved with physical distribution?
      \begin{enumerate}
        \item Packaging
        \item Order Processing
        \item Transportation
        \item Inventory Control
        \item Customer Service
        \item Materials
        \item Logistics
      \end{enumerate}
\end{enumerate}

\subsection{Critical Thinking Questions}

\begin{enumerate}
  \item Some business people believe that elimination agents and wholesalers
    reduce their operating expenses. Discuss the opportunity costs associated
    with eliminating intermediaries.
      \bf{The less people that are involved in the sale of goods, the less
      markup there is. Each person the goods pass through, that makes the price
      go up. Less intermediaries makes the price not as high.}
  \item As an importer of clothing, would you rather have your products sold by
    a general merchandise retailer or a specialty store? Why?
      \bf{Specialty Store. Because specialty stores are more expensive. So, if I
      have a specialty store sell my items, I will most likely make more profit.}
  \item Describe how a company would balance the tradeoff between cost and speed
    when selecting a shipping method.
      \bf{When deciding on which option to choose, we always look at the option
      which has a lower opportunity cost. So we can say that they are the most
    desirable trade-off}
  \item What are the effects of geography, time zones, work days, resources, and
    natural harbors on global business?
      \paragraph{Geography:} The geography of the country can make a difference
        when you are trying to ship to another country. For example, the ocean may
        be very dangerous and risky, so you will have to use a plane or a train to
        move your items.
      \paragraph{Time Zones:} It can be very difficult especially when you want
        to contact someone from another country like your agent, and for you, it's
        day and for them, it's like 3 in the morning. It would be very hard for
        either you or your agent to deal with each other.
\end{enumerate}

