\subsection{How to Make Choosing Easier}

\begin{enumerate}
  \item How many choices do people make in a given day? What choices do you make
    each day? \\
    \bf{Typically, a person will make about $70$ choices within a typical day.}
  \item What is the \it{"choice overload problem"}? \\
    \begin{definition}[Choice Overload Problem]
      This describes how, when you give a person more options to choose from,
      he/she will have a harder time to make a decision. And when they do make a
      decision, they might end up regretting their decision.
    \end{definition}
  \item Why do you think people have so many problems making choices? \\
    \bf{I think because they have so many options to choose from and they have
    such little time to choose, they just end up going with their gut and
    sometimes that's wrong.}
  \item What are the negatives to having too many choices? \\
    \bf{It just simply makes you feel way to overwhelmed. Then, once you make a
    decision, there's a high chance of you actually regretting it.}
  \item What are some ways that businesses can overcome the "choice overload \\
    problem"? \\
    \begin{enumerate}
      \item Cut
      \item Concretization
      \item Categorization
      \item Condition for complexity
    \end{enumerate}
\end{enumerate}

\subsection{What Consumers Want}

\begin{enumerate}
  \item What is customization? \\
    \begin{definition}[Customization]
      When you modify something to make it appeal/suit a specific individual or
      task.
    \end{definition}
  \item What is the experience economy? \\
    \begin{definition}[Experience Economy]
      An economy where most of the goods/services are sold by emphasizing the
      effect they can have the person's live.
    \end{definition}
  \item What does it mean for a product or service to be \it{"real real"}? \\
    \bf{Being what you say to others.}
\end{enumerate}
