\section*{Part A}
\label{sec:part_a}

\begin{enumerate}
  \label{enum:questions}

  \item Which story did you read? \\
    \textbf{The Boarded Window} by \textit{Ambrose Bierce}, $1891$
  \item Describe the physical setting of the story. Which words or descriptions
    contribute to the emotional setting or mood? What is the mood that results
    from the author’s use of description? \\
      \textbf{The setting of the story is in the wilderness area near
        Cincinnati. The mood of the story is mysteries and suspenseful.}
  \item What is the theme? How do the final lines of the story influence the
    meaning or theme of the story? \\
      \textbf{I think the theme of the story is death, the supernatural and
        selection. I think the last paragraph of the story influences the fear of
        the beast and death.}
  \item What techniques does the author use to create a surprise ending? \\
      \textbf{The author used situational irony to create a surprise ending.}
  \item Were you surprised by the twist? If so, why? If not, what should the
    author have done to make the ending more surprising and effective? \\
      \textbf{I was surprised by the twist. I didn't really understand it, but
        from what I understand, I think the wife is still alive because when the
        Murlock wakes up from being unconscious, he notices that his wife has a
        piece of the panther's ear in between her teeth, meaning she might have fought
        back, which implies she's still alive.}
  \item What was your experience in reading this story? Did it evoke fear or
    physically have an effect on you? Why or why not? \\
      \textbf{It didn't cause any fear and any it didn't have an affect on me.
        The reason is because I could never put my self in Murlock's shoes,
        which is why I cannot feel or understand what he went through.}
\end{enumerate}

% section part_a (end)

\newpage

\section*{Part B}
\label{sec:part_b}

My favorite plot twist in the movie \textit{Shutter Island}. I think this type
of plot twist is \textbf{Discovery and Reversal}.

% section part_b (end)
