\title{Homework \#5} % Assignment title
\date{May 11 by 11:59pm}

\textbf{Jane Eyre suffered a terrible life that no one in the right mind would
  want to go through. She was abused, bullied, and suffered terrible losses like
  her parents and siblings died from typhus. But, the whole plot would change if
  she was rich and beautiful. She wouldn't have went through the whole process
  of becoming a better version of herself. Nobody would disrespect her. It will
  be quite the opposite really. Everybody would love to be her friend. She might
  even have people around her who cares about her. Finally, she would most
  likely never have been able to meet her husband, who she loves dearly.}

\textbf{As you read the story, you will notice how Jane Eyre changed throughout
  the book. She changes just like a women would change in real life. She
  becomes, self-sufficient. What helped her was becoming a governess and then a
  headmistress of her school. Finally, she became very wealthy from her
  inheritance. She also starts to create her own values by the morals that she's
  gained over the years. Lastly, she has become a very mature women. She's happy
  with what she has become and she feels that she's finally equal with her
  husband, Mr. Rochester.} \cite{noauthor_jane_nodate}
  \textbf{Now, let's imagine she was grown up in a wealthy home, with beautiful
  sisters, including her. She wouldn't have to get her own morals and values.
  The parents would force their morals and values onto her. She would not have
  felt the same way as if she made her own morals and values. The same thing
  with everything else. She wouldn't be happy with the wealth that she has because
  she didn't earn it.}

\textbf{Most of Jane Eyre's life was living with abusive people. When she lived
  at the Gateshead Hall in her childhood, she would always be punished for things
  that she never did. Here's an incident that occurred while she was living in the
  Gateshead Hall.}

\begin{quotation}
  You think I have no feelings, and that I can live without one bit of love or
  kindness; but I cannot live so; and you have no pity. I shall remember how you
  thrust me back—roughly and violently thrust me back into the red-room, and
  locked me up there—to my dying day; though I was in agony; \ldots And that punishment
  you made me suffer because your wicked boy struck me \ldots People think you a good
  woman; but you are bad—hard-hearted. \cite{charlotte_project_1998}
\end{quotation}

\noindent \textbf{She was put in the red-room because she stood up to her cousin
  beating her up. So, her aunt put her in there to punish her. The red-room is
  where her uncle died in. Initially, Jane was just upset about how unjust her
  aunt was, but eventually, she started to imagine how upset her uncle feels
  about how his sister treats his family. She thought he would be so upset, that
  he would come back alive. Eventually, she went unconscious because she got to
  scared. She is also abused in other places. Like at her school, Lowood
  School and when she became governess at Thornfield Hall. Now, if she was
  beautiful and wealth, as she desired, she would never have went through all of
  the abuse that she had to endure. If somebody tried to abuse her and she had
  her loved ones around, like her parents, they would sue them because they would
  have the means to do so. Not only will everybody not try to mess with her, but
  they will try to become her friends. They will want to hang out more, go
  shopping, go to each other's houses, etc.}

\textbf{Jane Eyre met her husband when walking back home.}

\begin{quotation}
  On her way back from a walk, she meets Mr Rochester for the first time. His
  horse slips on the ice and falls, and Jane has to help him. Still unaware of who
  he is, she is amazed on returning home to discover that the gentleman she met is
  in fact her employer. \cite{charlotte_project_1998}
\end{quotation}

\noindent \textbf{The reason why she loves him is because she sees him as her emotional
  home. The reason is because she hasn't had anybody to love and for anybody to
  reciprocate that love. So, if she was beautiful and wealthy, like she wished,
  she most likely have met another man. But, even if she still happened to meet
  Mr. Rochester, there's a high probability that she won't love him like she did
  when she was poor.}

\textbf{In conclusion, Jane Eyre would have been a completely different
  character. This includes having a different personality, mind set, the way she
  views things, what she likes and dislikes, her feelings, and her husband. So,
  in essence, it's a great thing that she went through what she did because that
  toughened her up, made her develop herself, and see the world for what it really
  is. And finally, she met the love of her life, and they both lived happily
  together.}
