\begin{enumerate}
  \label{enum:questions}

  \item Guide to New Historicism and Cultural Studies \\
    \begin{enumerate}
      \label{enum:questions_1}
    
      \item What in the text indicates historical events? \\
          \textbf{In the beginning of the story, it says that the migration west.} \\
      \item What in the text would not fit in a different time period? \\
        \textbf{When Murlock was going to bury his wife without letting his friends,
          family, etc know, without having a doctor around for miles, him having to
          create the coffin, etc, would only fit in a time period that didn't have
          any communication system.}
      \item What in the text indicates the beliefs and values of the author? \\
        \textbf{When he referred to the process as a "sacred duty" probably
        indicates that he was religious.}
    \end{enumerate}
  \item Guide to Feminist Criticism \\
    \begin{enumerate}
      \label{enum:questions_2}
    
      \item What in the text concerns women or marriage? \\
          \textbf{"In that eastern country whence he came he had married, as was
          the fashion, a young woman in all ways worthy of his honest devotion,
          who shard the dangers and privations of his lot with a willing spirit and
          light hear."}
      \item What in the text indicates the writer is male or female? \\
          \textbf{The author says that he was a "well-informed boy", which implies
            that he's a male.}
      \item What in the text indicates assumptions about women and female roles
        in society? \\
          \textbf{The text says that Murlock's wife shared the dangers and
            privations of his lot with a willing spirit and light heart. That
            means that women back on those days had to agree with everything that
            their husband said or did, regardless if they really agree or not.}
    \end{enumerate}
  \item Guide to Psychoanalytic Criticism \\
    \begin{enumerate}
      \label{enum:questions_3}
    
      \item What in the text explains what the main character is thinking? \\
          \textbf{"She is dead, of course, but it is all right", means that
            Murlock was saddened by his wife's death, but he thought everything
            was going to be alright.}
      \item What in the text might be symbolic of underlying feelings or
        thoughts? \\
          \textbf{The author said that he tried to stay strong after her death
          by repeating that everything is going to be alright over and over.}
      \item What in the text depends on irrational fears or beliefs? \\
          \textbf{"He tried vainly to speak the dead woman's name, vainly to
            stretch forth his hand across the table to learn if she were there."}
    \end{enumerate}
\end{enumerate}
