%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                              Template                               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{wrong}
  This is an example \textbf{wrong} environment.
\end{wrong}

\begin{correct}
  This is an example \textbf{correct} environment.
\end{correct}

\begin{info}
  This is an example \textbf{info} environment.
\end{info}

\begin{warning}
  This is an example \textbf{warning} environment.
\end{warning}

\begin{caution}
  This is an example \textbf{caution} environment.
\end{caution}

\begin{terminology}
  This is an example \textbf{terminology} environment.
\end{terminology}

\begin{quote}
  This is an example \textbf{quote} environment.
\end{quote}

\begin{question}
  This is an example \textbf{question} environment.
\end{question}

\begin{confusion}
  This is an example \textbf{confusion} environment.
\end{confusion}

\begin{answer}
  This is an example \textbf{answer} environment.
\end{answer}

\begin{remark}
  This is an example \textbf{remark} environment.
\end{remark}

\begin{todo}
  This is an example \textbf{todo} environment.
\end{todo}

\begin{idea}
  This is an example \textbf{idea} environment.
\end{idea}

\begin{claim}
  This is an example \textbf{claim} environment.
\end{claim}

\begin{definition}
  This is an example \textbf{definition} environment.
\end{definition}

\begin{problem}
  This is an example \textbf{problem} environment.
\end{problem}

\begin{example}
  This is an example \textbf{example} environment.
\end{example}

URL Reference: \urlref{https://arxiv.org/pdf/2206.04059.pdf}{The disturbed outer Milky Way disc}

Offline Reference: \pdfref{master}{43}{master notes}
